\documentclass[12pt]{article}

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{graphics}
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{xspace}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage{hhline}
\usepackage{multirow}

\usepackage{pgfgantt}
\usepackage{rotating}
\usepackage[graphicx]{realboxes}
\usepackage{lscape}
\usepackage[margin=0.5in,landscape]{geometry}


\def\pgfcalendarweekdayletter#1{%  
 \ifcase#1M\or Tu\or W\or Tr\or F\or Sa\or Su\fi%  
}  
\usepackage{amsmath}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}

\newcommand{\SN}{S$_N$}
\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
\newcommand{\grad}{\vec{\nabla}} % gradient
\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\graphicspath{ {images/} }
\usepackage[affil-it]{authblk}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes }
\usepackage{cleveref}

\usepackage{datatool}
\usepackage[acronym,toc]{glossaries}
\include{acros}
	
\makeglossaries

\title{Modeling Methods for Initiating Events in Nuclear Spent Fuel Repositories}
\author{Jin Whan Bae}
\affil{Dept. of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign
		  Urbana, IL}
\date{}                     %% if you don't need date to appear
\setcounter{Maxaffil}{0}
\renewcommand\Affilfont{\itshape\small}
%%%%%%%%%%%%%%actual words%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\begin{document}
\maketitle

\section{Abstract}
\gls{UNF} repositories, given the high decay heat and radioactivity
of \glspl{UNF}, requires careful engineering. The current plan is
to design a repository that would contain the material for one million years.
Considering various events (failures) can occur in that time range,
the \gls{UNF} repository proposes an interesting subject for
\gls{PRA}. In this report, the model repository design is after the 
\gls{YMR}, which is a mined repository in volcanic tuff.
Ultimate failure status can be defined in various ways, depending on the
extent of leakage during the one million years (leakage from canister
\textasciitilde exposure to nearest population).
A definitive exposure of failure criteria must be defined,
in order for a reasonable analysis.  

Given the expansive
time range, very little real data is available.
Major issues or potential failures of the \gls{YMR} include volcanic activity
and canister failure. The two events have an extremely low
probability, but have catastrophic consequences. Considering that
risk is a function of both frequency and severity, the risk 
of the two factors is significant. 

This project summarizes literature on methods of modeling
initiating events of \gls{YMR}. Past research exists on using quantitative
assessment framework integrating the inference process
of Bayesian network \cite{lee_application_2006}, modeling
magma-drift interaction to predict volcanic and repository
failure events \cite{woods_modeling_2002}, and
using a homogeneous Poisson process \cite{ho_risk_1992}.


\section{Schedule}
\noindent\resizebox{\textwidth}{!}{
\begin{tikzpicture}[x=.5cm, y=1cm]
\begin{ganttchart}[
    hgrid,
    vgrid,
    group label font=\Large,
    progress=today,
    today=2017-11-10,
    x unit=6mm,
    newline shortcut=true,
    bar label node/.append style={align=right},
    time slot format=isodate
    ]{2017-11-10}{2017-12-21}
    \gantttitlecalendar{year, month=name, day, week=1, weekday=letter} \\
    
    \ganttgroup{Extended Abstract}{2017-11-10}{2017-11-23} \\
    \ganttbar{Literature Curation \ganttalignnewline Goal Definition}{2017-11-10}{2017-11-13} \\
    \ganttbar{Preliminary Analysis}{2017-11-16}{2017-11-23} \\

    
    \ganttgroup{Bayesian Network}{2017-11-23}{2017-11-25} \\
    \ganttgroup{Modeling Physical Phenomena}{2017-11-26}{2017-11-28}\\
    \ganttgroup{Homogeneous Poisson Process}{2017-11-29}{2017-11-30}\\
    \ganttgroup{Documentation and Report Write-up}{2017-12-01}{2017-12-10}\\
    \ganttbar{Document Result}{2017-12-01}{2017-12-10} \\
    
    

    
\end{ganttchart}
\end{tikzpicture}
}


\section{Background}
\gls{YMR} has been studied thoroughly in hopes of finally
disposing the U.S. \gls{UNF} inventory. However, considering
that it is a large project involving highly radioactive material,
careful planning and analyses must be done. The reference design
is taken from various sources \cite{u.s._department_of_energy_office_of_civilian_radioactive_waste_management_national_2008, wilson_total-system_1994, rechard_evolution_2014, u.s._department_of_energy_yucca_2002}.
Major sources of risk events are identified along with different ways to model
the events. 

Among them, certain initiating events are identified to be extremely difficult
to model using traditional risk analysis models, which calls for different
ways to model such rare and unpredictable events. 


\section{Literature Review}
System designs of the \gls{YMR} are listed extensively in literature \cite{u.s._department_of_energy_office_of_civilian_radioactive_waste_management_national_2008, wilson_total-system_1994, rechard_evolution_2014, u.s._department_of_energy_yucca_2002}, and contain multiple
iterations on the design. The basic design is as follows: the spent fuel assemblies
are repackaged in the waste package canister, and then placed underground,
underneath a drip shield. The canisters will remain there for up to millions of years,
surrounded by volcanic tuff.

Some prominent risk factors have also been identified. Volcanic hazards \cite{ho_risk_1992, smith_area_1990}
have been identified to be a long-term issue. Groundwater movement and transport of 
radioactive isotopes are another issue, in the case of canister breach \cite{robison_ground-water_1984, quade_fossil_1995}.  Canister reliability is another
identified risk factor \cite{whipple_can_1996, rutqvist_analysis_2003}.

Different aspects of risk analysis for nuclear waste repositories are published.
For systems where the future is hardly predictable, bayesian network analyses are 
suggested in \cite{lee_application_2006}. A method for sensitivity analysis
to rank important parameters are suggested in \cite{mohanty_cdf_2001}.


\section{Method}

For various facilities and aspects of the \gls{YMR}, events that
cannot be modeled with traditional risk analysis methods are picked.
Those events are carefully analyzed and defined to find an adequate
method to model the events. Various literature will be curated for
reference.

\section{Definition of System Failure}
The definition of `System Failure' as a whole is tricky, but for this analysis it is defined
as `Radioactive Material Escape from Container.'
`Radioactive Material' would namely mean the spent fuel assemblies.
The container could be the transport cask which transports the assemblies from
the reactors to the site, or the emplacement cask, which is ultimately put in the repository.

\section{Definition of Initiating Event}
An initiating event is what causes a cascade of events that eventually leads
to the system failure, which is defined above as `Radioactive Material Escape
from Container'. Examples of initiating events are volcanic activity and 
earthquakes.

\section{System Analysis}
In order to identify the various initiating events, a thorough system analysis
is done. Among them, weaker points are emphasized to find the most severe
initiating event that will affect multiple facilities or components. 

Initiating events have been identified as crucial to the 
\gls{YMR} system are listed in table \ref{tab:ie}.

\begin{table}[h]
    \centering
%   \scalebox{0.86}{
        \begin{tabular}{ccc}
            \hline
            \textbf{Initiating Event} & \textbf{Reason} & \textbf{Difficulty to Model} \\ \hline
            Volcanic Activity & Repository rupture and Large Heat Influx & Rare event and needs modeling of physical phenomena \\ 
            Canister Corrodes Away & Leakage of Radioactive material & Modeling corrosion in geological time periods \\
            Seismic Activity & Repository rupture & Rare event and difficult to predict \\ \hline
        \end{tabular}
        \caption{List of initiating events crucial to the failure of the \gls{YMR}}
        \label{tab:ie}
\end {table}
\FloatBarrier

\FloatBarrier



\bibliographystyle{unsrtnat}
\bibliography{bibliography}


\end{document}
\grid
